---
title: "Illinois Pre-processing"
output: html_notebook
---

## Group A

Read in each dataframe:
```{r}
library(readxl)

root = "C:\\Users\\User\\OneDrive - University College Cork\\Documents\\MSc\\Thesis\\TwoGroupsOfCowsData\\File S1\\GPS data of Group A\\"

groupA.files = list.files(path = root)

for(i in 1:length(groupA.files)) {                              # Head of for-loop
  assign(paste0("GroupA", i, '.df'),                                   # Read and store data frames
         read_excel(paste0(root, groupA.files[i])))
}
```
Get list of id numbers:
```{r}
groupA.ids = vector('character', 24)
for(i in 1:length(groupA.files)) {
  groupA.ids[i] = substr(groupA.files[i], 1, 4)
}
```

Add id numbers to dataframes:
```{r}
GroupA1.df$idnum = groupA.ids[1]
GroupA2.df$idnum = groupA.ids[2]
GroupA3.df$idnum = groupA.ids[3]
GroupA4.df$idnum = groupA.ids[4]
GroupA5.df$idnum = groupA.ids[5]
GroupA6.df$idnum = groupA.ids[6]
GroupA7.df$idnum = groupA.ids[7]
GroupA8.df$idnum = groupA.ids[8]
GroupA9.df$idnum = groupA.ids[9]
GroupA10.df$idnum = groupA.ids[10]
GroupA11.df$idnum = groupA.ids[11]
GroupA12.df$idnum = groupA.ids[12]
GroupA13.df$idnum = groupA.ids[13]
GroupA14.df$idnum = groupA.ids[14]
GroupA15.df$idnum = groupA.ids[15]
GroupA16.df$idnum = groupA.ids[16]
GroupA17.df$idnum = groupA.ids[17]
GroupA18.df$idnum = groupA.ids[18]
GroupA19.df$idnum = groupA.ids[19]
GroupA20.df$idnum = groupA.ids[20]
GroupA21.df$idnum = groupA.ids[21]
GroupA22.df$idnum = groupA.ids[22]
GroupA23.df$idnum = groupA.ids[23]
GroupA24.df$idnum = groupA.ids[24]
```

Cows X011 (3) and X004 (2) have variable 'Time' instead of 'time':
```{r}
library(dplyr)

GroupA2.df = GroupA2.df %>% rename(time = Time)
GroupA3.df = GroupA3.df %>% rename(time = Time)
```

Merge dataframes:
```{r}
#put all data frames into list
df_listA <- list(GroupA1.df, GroupA2.df, GroupA3.df, GroupA4.df, GroupA5.df, GroupA6.df, GroupA7.df, GroupA8.df, GroupA9.df, GroupA10.df, GroupA11.df, GroupA12.df, GroupA13.df, GroupA14.df, GroupA15.df, GroupA16.df, GroupA17.df, GroupA18.df, GroupA19.df, GroupA20.df, GroupA21.df, GroupA22.df, GroupA23.df, GroupA24.df)      

#merge all data frames together
GroupA.df = Reduce(function(x, y) merge(x, y, all=TRUE), df_listA)
```

Convert time from seconds to POSIXct:
```{r}
#run only once!
GroupA.df$time.seconds <- GroupA.df$time

library(lubridate)
GroupA.df$time = as_datetime(GroupA.df$time, origin = '2011-06-02 00:00:00 CST')
```

Day/night split:
-	June 2nd 2011 – sunrise 05:25, sunset 20:16
-	June 10th 2011 – sunrise 05:23, sunset 20:21

Set: sunrise 05:20, sunset 20:20

```{r}
GroupA.times = vector('character', nrow(GroupA.df))
for(i in 1:nrow(GroupA.df)){
  time.hms = format(GroupA.df$time[i], format = '%H:%M:%S')
  if(time.hms >= '05:20:00' & time.hms <= '20:20:00'){
    GroupA.times[i] = 'day'
  }
  else{
    GroupA.times[i] = 'night'
  }
}

#add column to data frame
GroupA.df$day.night = GroupA.times
```

```{r}
#Split data by day/night
GroupA.day.df <- GroupA.df[which(GroupA.df$day.night == 'day'), ]
GroupA.night.df <- GroupA.df[which(GroupA.df$day.night == 'night'), ]
```

## Group B

code from https://statisticsglobe.com/r-write-read-multiple-csv-files-for-loop :
```{r}
root = "C:\\Users\\User\\OneDrive - University College Cork\\Documents\\MSc\\Thesis\\TwoGroupsOfCowsData\\File S1\\GPS data of Group B\\"

groupB.files = list.files(path = root)

for(i in 1:length(groupB.files)) {                              # Head of for-loop
  assign(paste0("GroupB", i, '.df'),                                   # Read and store data frames
         read_excel(paste0(root, groupB.files[i])))
}
```

```{r}
#Add ID numbers to data frames
groupB.ids = vector('character', 8)
for(i in 1:length(groupB.files)) {
  groupB.ids[i] = substr(groupB.files[i], 1, 5)
}

GroupB1.df$idnum = groupB.ids[1]
GroupB2.df$idnum = groupB.ids[2]
GroupB3.df$idnum = groupB.ids[3]
GroupB4.df$idnum = groupB.ids[4]
GroupB5.df$idnum = groupB.ids[5]
GroupB6.df$idnum = groupB.ids[6]
GroupB7.df$idnum = groupB.ids[7]
GroupB8.df$idnum = groupB.ids[8]
```

Merge groups:
(code from https://www.statology.org/merge-multiple-data-frames-in-r/)
```{r}
#put all data frames into list
df_list <- list(GroupB1.df, GroupB2.df, GroupB3.df, GroupB4.df, GroupB5.df, GroupB6.df, GroupB7.df, GroupB8.df)      

#merge all data frames together
GroupB.all.df = Reduce(function(x, y) merge(x, y, all=TRUE), df_list)  
```

Convert time from seconds to POSIXct:
```{r}
#run only once!
GroupB.all.df$time.seconds <- GroupB.all.df$Time

library(lubridate)
#library(data.table)

#as_datetime(seconds, origin = '2011-10-24 10:00:00 CST')
GroupB.all.df$Time = as_datetime(GroupB.all.df$Time, origin = '2011-10-24 00:00:00')
```


daytime/nighttime split:

-	Oct 24th  2011 – sunrise 07:16, sunset 18:05
-	Oct 28th  2011 – sunrise 07:20, sunset 18:00

set: sunrise 07:15, sunset 18:00.

```{r}
GroupB.times = vector('character', nrow(GroupB.all.df))
for(i in 1:nrow(GroupB.all.df)){
  time.hms = format(GroupB.all.df$Time[i], format = '%H:%M:%S')
  if(time.hms >= '07:15:00' & time.hms <= '18:00:00'){
    GroupB.times[i] = 'day'
  }
  else{
    GroupB.times[i] = 'night'
  }
}

#add column to data frame
GroupB.all.df$day.night = GroupB.times
```

```{r}
#Split data by day/night
GroupB.day.df <- GroupB.all.df[which(GroupB.all.df$day.night == 'day'), ]
GroupB.night.df <- GroupB.all.df[which(GroupB.all.df$day.night == 'night'), ]
```


