---
title: "Illinois Pairwise Distances 2"
output: html_notebook
---

Consider daytime only

8C2 = 28 (28 pairs in a group of 8).
24C2 = 276 (276 pairs in a group of 24).

## Group B

Create pairs:

```{r}
library(combinat)

GroupB.pairs = combn(groupB.ids, 2)
```

Use spatsoc to create temporal groups:
```{r}
library(data.table)
GroupB.day.dt = setDT(GroupB.day.df)

library(spatsoc)

group_times(GroupB.day.dt, datetime = 'Time', threshold = '4 minutes')
```

```{r}
timegroupsB = unique(GroupB.day.dt$timegroup)
```

Plot pairwise distances for each pair:
```{r}
par(mfrow=c(2,2))
for(i in 1:28){
  pair.id1 = GroupB.pairs[1, i]
  pair.id2 = GroupB.pairs[2, i]
  
  pair.1 = GroupB.day.dt[which(GroupB.day.dt$idnum == pair.id1),]
  pair.2 = GroupB.day.dt[which(GroupB.day.dt$idnum == pair.id2),]
  
  pair.dists = vector(mode = 'numeric', length = length(timegroupsB))
  
  for(i in 1:length(timegroupsB)){
    X.1 = pair.1[which(pair.1$timegroup == timegroupsB[i]),]$X
    Y.1 = pair.1[which(pair.1$timegroup == timegroupsB[i]),]$Y
    X.2 = pair.2[which(pair.2$timegroup == timegroupsB[i]),]$X
    Y.2 = pair.2[which(pair.2$timegroup == timegroupsB[i]),]$Y
    dist = sqrt(((X.1-X.2)**2)+((Y.1-Y.2)**2))
    # account for 0 or more than one recordings at a timegroup
    if(length(dist) == 1){
      pair.dists[i] = dist
    } else if(length(dist) == 0){
      pair.dists[i] = NA
    } else{
      pair.dists[i] = mean(dist)
    }
  }
  plot(pair.dists, ylim = c(0, 300), main = paste(pair.id1, 'and', pair.id2, ': Distance over Time'))
  abline(h = median(pair.dists, na.rm = TRUE), col=2)
  abline(h = mean(pair.dists, na.rm = TRUE), col=3)
}
par(mfrow=c(1,1))
```

Get mean+median distance for all pairs:
```{r}
pairsB = c() #vector(mode = 'character', length= 28)
meanB = c() #vector(mode = 'numeric', length = 28)
medianB = c() #vector(mode = 'numeric', length = 28)

for(i in 1:28){
  pair.id1 = GroupB.pairs[1, i]
  pair.id2 = GroupB.pairs[2, i]
  
  pair.1 = GroupB.day.dt[which(GroupB.day.dt$idnum == pair.id1),]
  pair.2 = GroupB.day.dt[which(GroupB.day.dt$idnum == pair.id2),]
  
  pair.dists = vector(mode = 'numeric', length = length(timegroupsB))
  
  for(i in 1:length(timegroupsB)){
    X.1 = pair.1[which(pair.1$timegroup == timegroupsB[i]),]$X
    Y.1 = pair.1[which(pair.1$timegroup == timegroupsB[i]),]$Y
    X.2 = pair.2[which(pair.2$timegroup == timegroupsB[i]),]$X
    Y.2 = pair.2[which(pair.2$timegroup == timegroupsB[i]),]$Y
    dist = sqrt(((X.1-X.2)**2)+((Y.1-Y.2)**2))
    # account for 0 or more than one recordings at a timegroup
    if(length(dist) == 1){
      pair.dists[i] = dist
    } else if(length(dist) == 0){
      pair.dists[i] = NA
    } else{
      pair.dists[i] = mean(dist)
    }
  }
  
  pairsB <- append(pairsB, paste(pair.id1, 'and', pair.id2))
  meanB <- append(meanB, mean(pair.dists, na.rm = TRUE))
  medianB <- append(medianB, median(pair.dists, na.rm = TRUE))
}

pair_distsB.df <- data.frame(pairsB, meanB, medianB)
pair_distsB.df
```

Create heatmap of means and medians:
```{r}
pair_distsB.mean.mat <- matrix(1:64, nrow=8, dimnames = list(groupB.ids, groupB.ids))
pair_distsB.median.mat <- matrix(1:64, nrow=8, dimnames = list(groupB.ids, groupB.ids))

#set diagonal to 0
for(i in 1:8){
  pair_distsB.mean.mat[i, i] = 0
  pair_distsB.median.mat[i, i] = 0
}
```

```{r}
#fill in means and medians
#x = pair_distsB.mean.mat
n = 8
m = 1
k = n-1
v = n-2

for(i in 1:(n-1)){
  l = i+1
  pair_distsB.mean.mat[l:n, i] = meanB[m:k]
  pair_distsB.mean.mat[i, l:n] = meanB[m:k]
  pair_distsB.median.mat[l:n, i] = medianB[m:k]
  pair_distsB.median.mat[i, l:n] = medianB[m:k]
  m = k + 1
  k = k + v
  v = v - 1
}
```

```{r}
par(mfrow=c(2,2))

heatmap(pair_distsB.mean.mat, Rowv = NA, Colv = NA, symm = T, main = 'Mean Pairwise Distance')
#legend(x='right', legend=c("min", "med", "max"), fill=heat.colors(3))

heatmap(pair_distsB.median.mat, Rowv = NA, Colv = NA, symm = T, main = 'Median Pairwise Distance')
#legend(x='right')

par(mfrow=c(1,1))
```

pheatmap:
```{r}
library(pheatmap)
#library(viridis)
#library(ggplot2)

b <- 0:50
#my.col <- scale_colour_gradientn(colours = rev(c("darkred", "orange", "yellow", "white")))

pheatmap(pair_distsB.mean.mat, color = colorRampPalette(c('black','red', 'yellow'))(20), cluster_cols = F, cluster_rows = F, treeheight_col = 0, treeheight_row = 0, cellwidth= 33, cellheight = 33, main = 'Mean Pairwise Distance - Group B')

pheatmap(pair_distsB.median.mat, color = colorRampPalette(c('black','red', 'yellow'))(20), cluster_cols = F, cluster_rows = F, treeheight_col = 0, treeheight_row = 0, cellwidth= 33, cellheight = 33, main = 'Median Pairwise Distance - Group B All Days')
#color = inferno(10, direction= -1)
```


## Group A

Create pairs:

```{r}
library(combinat)

GroupA.pairs = combn(groupA.ids, 2)
```

Use spatsoc to create temporal groups:
```{r}
library(data.table)
GroupA.day.dt = setDT(GroupA.day.df)

library(spatsoc)

group_times(GroupA.day.dt, datetime = 'time', threshold = '4 minutes')
```

```{r}
timegroupsA = unique(GroupA.day.dt$timegroup)
```

Too many pairs to plot all.

Get mean+median distance for all pairs:
```{r}
pairsA = c() 
meanA = c() 
medianA = c() 

for(i in 1:276){
  pair.id1 = GroupA.pairs[1, i]
  pair.id2 = GroupA.pairs[2, i]
  
  pair.1 = GroupA.day.dt[which(GroupA.day.dt$idnum == pair.id1),]
  pair.2 = GroupA.day.dt[which(GroupA.day.dt$idnum == pair.id2),]
  
  pair.dists = vector(mode = 'numeric', length = length(timegroupsA))
  
  for(i in 1:length(timegroupsA)){
    X.1 = pair.1[which(pair.1$timegroup == timegroupsA[i]),]$X
    Y.1 = pair.1[which(pair.1$timegroup == timegroupsA[i]),]$Y
    X.2 = pair.2[which(pair.2$timegroup == timegroupsA[i]),]$X
    Y.2 = pair.2[which(pair.2$timegroup == timegroupsA[i]),]$Y
    dist = sqrt(((X.1-X.2)**2)+((Y.1-Y.2)**2))
    # account for 0 or more than one recordings at a timegroup
    if(length(dist) == 1){
      pair.dists[i] = dist
    } else if(length(dist) == 0){
      pair.dists[i] = NA
    } else{
      pair.dists[i] = mean(dist)
    }
  }
  
  pairsA <- append(pairsA, paste(pair.id1, 'and', pair.id2))
  meanA <- append(meanA, mean(pair.dists, na.rm = TRUE))
  medianA <- append(medianA, median(pair.dists, na.rm = TRUE))
}

pair_distsA.df <- data.frame(pairsA, meanA, medianA)
pair_distsA.df
```

Create heatmap of means and medians:
```{r}
pair_distsA.mean.mat <- matrix(1:576, nrow=24, dimnames = list(groupA.ids, groupA.ids))
pair_distsA.median.mat <- matrix(1:576, nrow=24, dimnames = list(groupA.ids, groupA.ids))

#set diagonal to 0
for(i in 1:24){
  pair_distsA.mean.mat[i, i] = 0
  pair_distsA.median.mat[i, i] = 0
}
```

```{r}
#fill in means and medians
#x = pair_distsA.mean.mat
n = 24
m = 1
k = n-1
v = n-2

for(i in 1:(n-1)){
  l = i+1
  pair_distsA.mean.mat[l:n, i] = meanA[m:k]
  pair_distsA.mean.mat[i, l:n] = meanA[m:k]
  pair_distsA.median.mat[l:n, i] = medianA[m:k]
  pair_distsA.median.mat[i, l:n] = medianA[m:k]
  m = k + 1
  k = k + v
  v = v - 1
}
```

```{r}
library(pheatmap)

pheatmap(pair_distsA.mean.mat, color = colorRampPalette(c('black','red', 'yellow'))(20), cluster_cols = F, cluster_rows = F, treeheight_col = 0, cellwidth= 11, cellheight = 11, treeheight_row = 0, main = 'Mean Pairwise Distance - Group A (not clustered)')

pheatmap(pair_distsA.median.mat, color = colorRampPalette(c('black','red', 'yellow'))(20), cluster_cols = F, cluster_rows = F, treeheight_col = 0, cellwidth= 11, cellheight = 11, treeheight_row = 0, main = 'Median Pairwise Distance - Group A All Days')

pheatmap(pair_distsA.mean.mat, color = colorRampPalette(c('black','red', 'yellow'))(20), treeheight_col = 0, treeheight_row = 0, cellwidth= 11, cellheight = 11, main = 'Mean Pairwise Distance - Group A (clustered)')

pheatmap(pair_distsA.median.mat, color = colorRampPalette(c('black','red', 'yellow'))(20), treeheight_col = 0, treeheight_row = 0, cellwidth= 11, cellheight = 11, main = 'Median Pairwise Distance - Group A (clustered)')
```

## Networks from pairwise-distance matrices

```{r}
# Group A

library(igraph)

#inverse since closer = better
pair_distsA.med = 1/pair_distsA.median.mat

#set inf to 0 (1/0 -> inf)
pair_distsA.med[is.infinite(pair_distsA.med)] <- 0

GroupA.graph.med <- graph.adjacency(pair_distsA.med, mode="undirected", weighted=TRUE)

#Color scaling function
c_scale <- colorRamp(c('white','grey','black'))

E(GroupA.graph.med)$weight <- (E(GroupA.graph.med)$weight/max(pair_distsA.med))

#Applying the color scale to edge weights.
#rgb method is to convert colors to a character vector.
E(GroupA.graph.med)$color = apply(c_scale(E(GroupA.graph.med)$weight), 1, function(x) rgb(x[1]/255,x[2]/255,x[3]/255) )

E(GroupA.graph.med)$weight <- (E(GroupA.graph.med)$weight*10)

plot(GroupA.graph.med, edge.width = E(GroupA.graph.med)$weight, edge.col = E(GroupA.graph.med)$color, layout=layout.fruchterman.reingold, main = 'Network of Median Pairwise Distance - Group A')
```

```{r}
# Group B

#inverse since closer = better
pair_distsB.med = 1/pair_distsB.median.mat

#set inf to 0 (1/0 -> inf)
pair_distsB.med[is.infinite(pair_distsB.med)] <- 0

GroupB.graph.med <- graph.adjacency(pair_distsB.med, mode="undirected", weighted=TRUE)

#Color scaling function
c_scale <- colorRamp(c('white','grey','black'))

E(GroupB.graph.med)$weight <- (E(GroupB.graph.med)$weight/max(pair_distsB.med))

#Applying the color scale to edge weights.
#rgb method is to convert colors to a character vector.
E(GroupB.graph.med)$color = apply(c_scale(E(GroupB.graph.med)$weight), 1, function(x) rgb(x[1]/255,x[2]/255,x[3]/255) )

E(GroupB.graph.med)$weight <- (E(GroupB.graph.med)$weight*10)

plot(GroupB.graph.med, edge.width = E(GroupB.graph.med)$weight, edge.col = E(GroupB.graph.med)$color, layout=layout.fruchterman.reingold, main = 'Network of Median Pairwise Distance - Group B')
```

## Node Strength

```{r}
#Group A (all days)
n = 24
PDistA.strength = vector(mode = 'numeric', length = n)

for(i in 1:length(groupA.ids)){
  soc = sum(pair_distsA.med[groupA.ids[i], ])
  PDistA.strength[i] = soc
}

pdiststrnA <- data.frame(groupA.ids, PDistA.strength)

#Group B (all days)
n = 8
PDistB.strength = vector(mode = 'numeric', length = n)

for(i in 1:length(groupB.ids)){
  soc = sum(pair_distsB.med[groupB.ids[i], ])
  PDistB.strength[i] = soc
}

pdiststrnB <- data.frame(groupB.ids, PDistB.strength)
```

#Group A graph 2:

Replace all values that are less than the mean with 0:
```{r}
pair_distsA.med2 = pair_distsA.med
for(i in 1:24){
  for(j in 1:24){
  if(pair_distsA.med[i,j] < mean(pair_distsA.med)){
    pair_distsA.med2[i,j] = 0
  }
  }
}
```

```{r}
#coordsA <- layout.fruchterman.reingold(GroupA.graph)

GroupA.graph.med2 <- graph.adjacency(pair_distsA.med2, mode="undirected", weighted=TRUE)

#Color scaling function
c_scale <- colorRamp(c('white','grey','black'))

E(GroupA.graph.med2)$weight <- (E(GroupA.graph.med2)$weight/max(pair_distsA.med2))

#Applying the color scale to edge weights.
#rgb method is to convert colors to a character vector.
E(GroupA.graph.med2)$color = apply(c_scale(E(GroupA.graph.med2)$weight), 1, function(x) rgb(x[1]/255,x[2]/255,x[3]/255) )

E(GroupA.graph.med2)$weight <- (E(GroupA.graph.med2)$weight*10)
V(GroupA.graph.med2)$size <- (PDistA.strength)*10

plot(GroupA.graph.med2, edge.width = E(GroupA.graph.med2)$weight, edge.col = E(GroupA.graph.med2)$color, layout=coordsA, main = 'Network of Median Pairwise Distance - Group A')
```
# Group B
```{r}
#coordsB <- layout.fruchterman.reingold(GroupB.graph)

GroupB.graph.med <- graph.adjacency(pair_distsB.med, mode="undirected", weighted=TRUE)

#Color scaling function
c_scale <- colorRamp(c('white','grey','black'))

E(GroupB.graph.med)$weight <- (E(GroupB.graph.med)$weight/max(pair_distsB.med))

#Applying the color scale to edge weights.
#rgb method is to convert colors to a character vector.
E(GroupB.graph.med)$color = apply(c_scale(E(GroupB.graph.med)$weight), 1, function(x) rgb(x[1]/255,x[2]/255,x[3]/255) )

E(GroupB.graph.med)$weight <- (E(GroupB.graph.med)$weight*10)
V(GroupB.graph.med)$size <- (PDistB.strength)*75

plot(GroupB.graph.med, edge.width = E(GroupB.graph.med)$weight, edge.col = E(GroupB.graph.med)$color, layout=coordsB, main = 'Network of Median Pairwise Distance - Group B')
```


